Supplementary Materials: Introductory Physics Labs: A Tale of Two Transformations

### 2020-10-02 supplement/supplement.tex
Finished experiment summaries for supplement.  Needs another set of eyes before sending off to TPT.

\section{Curriculum development timeline}
Talk about the curriculum development, and how departmental culture around the labs changed as
a part of this transformation.

@@

\section{Transformation \#1: Argument Driven Inquiry}
\subsection{Physics \textrm{I} Investigation 1}

\subsection{Physics \textrm{I} Investigation 2}

\subsection{Physics \textrm{I} Investigation 3}

\subsection{Physics \textrm{I} Investigation 4}

\subsection{Physics \textrm{II} Investigation 1}

\subsection{Physics \textrm{II} Investigation 2}

\subsection{Physics \textrm{II} Investigation 3}

\subsection{Physics \textrm{II} Investigation 4}

@@

Each group was required to complete its analysis and create a three-slide presentation for the
argumentation session the following week. The first slide was a description of their
measurements. Te second slide was a presentation of the results, including a graph or table,
and the third slide was their argument, based on their result.

>>>>

This supplement is meant to accompany the paper, \textit{Introductory Physics Labs: A Tale of
  Two Transformations} being submitted to \textit{The Physics Teacher}.  It is divided into the
following sections:
\begin{description}
  \item[Additional Instructional Context] discusses some particulars of our department and
  institution that can help the reader put the scope and population of the intervention into
  context.
  \item[Transformation \#1: Argument Driven Inquiry] provides a brief summary of each of the
  experiments done in the face-to-face version of this lab course.
  \item[Transformation \#2: Online delivery] provides a summary of how we adapted or created
  new activities for students to do their labs online, and discusses some of the ways that we
  supported authentic experimentation in this online environment.
\end{description}

@@

\section{Transformation \#1: Argument Driven Inquiry}
In each of the sections below, we provide a brief summary of the ADI curriculum that we have
implemented in our physics labs.  We will discuss the pre-lab reading, which students are
expected to complete before they arrive in lab.  We also discuss the supplies that we use,
especially when they are novel.  Every experiment requires a computer for data analysis.
However, most supplies that we use are found in a typical college physics lab, although this
isn't universally true.  (We do a radioactive decay lab that utilizes a PuBe neutron source.)
We will also discuss some common approaches used by students in the activity.

One last thing of note: Oftentimes, we have made choices that give students a significant
hurdle to overcome (e.g., you can't neglect friction).  Student data should be messy.  There
should be some things that are unclear.  When we teach physics labs, we can give our students
the illusion that lab science is done by following well-known procedures and produce pristine
data. However, the opposite can often be true. As you read some of these descriptions, you
probably will think of 10 ways that the experiments could be done, ``better''---be it with
different techniques or equipment.  That is the point.  We want to give students an idea to
start with, and then give them the freedom to make changes, try things out, and figure out
their own way of knowing.

\subsection{Physics \textrm{I} Investigation 1}
\begin{description}
  \item[Pre-lab reading] We provide a brief introduction to statistics, defining the terms
  average, standard deviation, and standard error.  We also discuss how to calculate those
  quantities in Excel.  We have a traditional discussion of how to use a ruler to measure
  distances, and end with a brief introduction to free-fall.
  \item[Pre-lab activity] We divide the room in half and have them measure the heights of all
  students, comparing the average heights of the students on the ``right'' and on the ``left''
  of the room.  We have them use a simple rule to compare their measurements, if the value
  $\pm$ uncertainty (standard error) overlaps for these measurements, then the measurements
  agree, otherwise, they disagree.
  \item[Supplies of note] Meter sticks and 2-meter sticks.
  \item[Argumentation Question] Do two people have the same reaction time?
  \item[Common student approaches] Most students drop meter sticks and catch them.  They
  measure the distance that the stick falls, and use the free-fall equation to relate distance
  fallen to time in free-fall.  Some find one of the myriad apps out there that will measure
  reaction time, such as the one at \url{https://humanbenchmark.com/}.  Note, not all apps are
  created equal.  
\end{description}

\subsection{Physics \textrm{I} Investigation 2}
\begin{description}
  \item[Pre-lab reading] We talk about how ultrasonic motion detectors work (schematically, not
  technically, and discuss how to calculate velocity from discrete position vs. time data. We
  finally discuss linear regression, how to interpret it on a basic level, and how it can be
  calculated in Excel.\footnote{Because we want our fit values to have uncertainties, we have
    our students install the \textit{Data Analysis Toolpack} if they are using Excel.}
  \item[Pre-lab activity] We give the students a cart and a track, have them incline that
  track, and have them measure the net force on the cart as it moves on the track.
  \item[Supplies of note] Ultrasonic motion detector, various masses, carts (with fan
  attachments), and a track.
  \item[Argumentation Question] Does the force that the fan exerts depend on the mass of the
  cart?
  \item[Common student approaches] Students measure the net force of a cart moving on a flat
  track under the influence of a fan several times, changing the mass of the cart each time.
  One particular struggle that students have is that they do not take friction into account,
  which is not negligible on this setup.
\end{description}

\subsection{Physics \textrm{I} Investigation 3}
\begin{description}
  \item[Pre-lab reading] We discuss strategies for linearizing non-linear data for well-known
  cases.
  \item[Pre-lab activity] We have the students measure the period of oscillation for a mass
  spring system, linearizing the data two ways, and comparing the spring constant for each of
  these analyses.
  \item[Supplies of note] Masses, springs, hangars, and a coiled snake (a spring with a
  non-negligible mass).
  \item[Argumentation Question] When does the spring's mass matter?
  \item[Common student approaches] Students use the traditional measure the time of 10
  oscillations and divide approach.  Other than that, experimental approaches are fairly
  uniform.  Different approaches to student analysis techniques are common and encouraged.
\end{description}

\subsection{Physics \textrm{I} Investigation 4}
\begin{description}
  \item[Pre-lab reading] We discuss collisions, and define momentum and kinetic energy.
  \item[Pre-lab activity] We have students analyze the motion of two objects on a video.  We
  have students use \textit{Tracker}\citep{bro2009} to quantify that motion.  Students then
  compare the motion of those two objects.
  \item[Supplies of note] Marbles and a meter stick.  And the students phones.  (We thought
  about getting a video camera for students to use, but realized that students already had one,
  and that camera already has a number of features built into it---such as picture
  steadying---that getting our own wasn't worth the effort.)
  \item[Argumentation Question] Is the collision between two marbles elastic?
  \item[Common student approaches] Students simply let marbles collide and videotape the
  action. Many of the problems here are on the data analysis end.  Friction is a killer here,
  and is an issue that students deal with differently in their data analyses.
\end{description}

\subsection{Physics \textrm{II} Investigation 1}
\begin{description}
  \item[Pre-lab reading] We review current, voltage, and resistance.  We also discuss how to
  use a multimeter.
  \item[Pre-lab activity] Measure the I-V curve of a resistor.
  \item[Supplies of note] Multimeters (2), lightbulb, resistor, power supply.
  \item[Argumentation Question] Does a lightbulb behave like a resistor?
  \item[Common student approaches] Students measure an I-V curve.  Sometimes the data is
  sort-of linear $(R^2\sim 0.9)$, and students have to deal with that.
\end{description}

\subsection{Physics \textrm{II} Investigation 2}
\begin{description}
  \item[Pre-lab reading] Students read about capacitance and voltage and are reminded
  \item[Pre-lab activity] Students measure the time constant for a RC circuit.
  \item[Supplies of note] We have created several RC circuit kits that are integrated so that
  the time constant is similar for all of the circuits without the bulb, then students can
  throw a switch to add a bulb to the circuit in series.  When added into the circuit, some of
  the bulbs light up, others do not. Multimeter, timer, power supply.
  \item[Argumentation Question] How does adding a light bulb in series change the behavior of a
  RC circuit?
  \item[Common student approaches] Measure the time constant for their kit.  See if $\tau$
  changes from the prelab.
\end{description}

\subsection{Physics \textrm{II} Investigation 3}
\begin{description}
  \item[Pre-lab reading] Students get a reading about diffraction and Babinet's principle.
  \item[Pre-lab activity] Students use one laser of known wavelength to measure a slit's width,
  then they use the same slit to measure the wavelength of an unknown laser.
  \item[Supplies of note] Optical bench, slit, lasers, screen.
  \item[Argumentation Question] Are hairs from different people the same diameter?
  \item[Common student approaches] Measure diffraction pattern of two hairs, use that to find
  the thickness of each and compare.
\end{description}

\subsection{Physics \textrm{II} Investigation 4}
\begin{description}
  \item[Pre-lab reading] Discussion of nuclear decay and Geiger counters.
  \item[Pre-lab activity] Students measure the ``decay constant'' of dice.
  \item[Supplies of note] We use a PuBe source to irradiate some copper pennies, and a geiger
  counter to measure the decay.
  \item[Argumentation Question] What isotope is most common in the nuclear decay of a penny?
  \item[Common student approaches] Students set up an appropriate enclosure and collect nuclear
  activity data.  The issue here is that copper has a double decay (two common isotopes), and
  the answer isn't straightforward.
\end{description}

@@

Each group was required to complete its analysis and create a three-slide presentation for the
argumentation session the following week. The first slide was a description of their
measurements. The second slide was a presentation of the results, including a graph or table,
and the third slide was their argument, based on their result.
